Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-24 edubots_surveys.Rnw
Adds interaction figure and rationale refs #17

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<gender, echo=FALSE>>=
ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

@@

% 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}

>>>>

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<gender, echo=FALSE>>=
ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

@@

% 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}
%
\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE>>=
library(forcats)
data %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

ggplot(Age.vs.Experience,aes(Age,Experience))+geom_point(aes(size=freq),colour="green")
@
\end{center}
\caption{Correlation between age and experience.}
\label{figure:age.vs.exp}
\end{figure}

Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar, and as a matter of fact, as Figure \ref{figure:age.vs.exp} age and experience are correlated strongly, with experience being roughly 20-30 years less than age. This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages. At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
